ms_figures

### 2024-05-01 ms_figures.Rmd
ms figures edits for manuscript edits

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(countrycode)
library(circlize)
library(here)
library(ggpubr)
library(kableExtra)
library(DBI)
library(janitor)
library(viridis)
library(broom)
library(exploreARTIS)
library(vegan)
library(tidytext)
library(cowplot)
library(scales)
library(ggsankey)
library(ggpubr)
```

```{r load_data}
# Set directories
datadir <- "qa/outputs_20240221"
outdir <- "qa/outputs_20240221"
```

@@

@@

fig1c_out_degree <- fig1c_data %>%
    mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))) %>%
  ggplot(aes(x = year, y = all_in_degree, color = habitat_method)) +
  geom_smooth(alpha = 0.2) +
  scale_color_manual(values = habitat_source_colors) +
  labs(y = "Average\nno. export partners", color = "Source") + 
  theme_bw() +
  theme(
    text = element_text(size = 10),
    axis.title.x = element_blank(),
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 6)
  )

@@

ggsave(file.path(outdir, "fig1.png"))
```

# Figure 2: Trade patterns

```{r fig2_data}
artis_region_method <- read.csv(file.path(datadir, "artis_region_method.csv"))
artis_region <- read.csv(file.path(datadir, "artis_region.csv"))
```

```{r fig2a}

region_net_import <- artis_region_method %>% 
  group_by(year, importer_region) %>%
  summarise(import_live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>%
  rename(region = importer_region) %>%
  left_join(artis_region_method %>% 
              group_by(year, exporter_region) %>%
              summarise(export_live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>%
              rename(region = exporter_region), by = c("year", "region")) %>%
  mutate(net_import = import_live_weight_t-export_live_weight_t)

fig2a <- ggplot() +
  geom_area(data = artis_region_method %>% 
                mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))) %>%
              select(-exporter_importer) %>%
              pivot_longer(exporter_region:importer_region, 
                           names_to = c("flow", "drop"), 
                           values_to = "region", names_sep = "_") %>% 
              filter(flow == "exporter") %>%
              group_by(year, region, habitat_method) %>%
              summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)), 
            aes(x = year, y = -1*live_weight_t/1000000, fill = habitat_method)) +
  geom_area(data = artis_region_method %>% 
                mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))) %>%
              select(-exporter_importer) %>%
              pivot_longer(exporter_region:importer_region, 
                           names_to = c("flow", "drop"), 
                           values_to = "region", names_sep = "_") %>% 
              filter(flow == "importer") %>%
              group_by(year, region, habitat_method) %>%
              summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)), 
            aes(x = year, y = live_weight_t/1000000, fill = habitat_method)) +
  scale_fill_manual(values = habitat_source_colors) +
  geom_hline(yintercept = 0, color = "black", linewidth = 0.5, linetype = "dashed") +
  geom_line(data = region_net_import, aes(x = year, y = net_import/1000000, color = "Net import"), linewidth = 1) +
  scale_color_manual(values = "black") +
  labs(x = "", y = "Trade (million t, live weight)", fill = "Source", color = "") +
  guides(fill = guide_legend(nrow = 2)) +
  theme_bw() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        strip.background = element_blank(),
        plot.margin = unit(c(t=0, r=1, b=0, l=0.5), "cm")) +
  facet_wrap(~region, nrow = 1)

fig2a <- ggdraw(fig2a) +
  draw_label("Net import", x = 0.97, y = 0.55, angle = 270, size = 9) +
  draw_label("Net export", x = 0.97, y = 0.3, angle = 270, size = 9)

fig2a
```

```{r fig2b}
# Matrix of plots showcasing inter-regional trade trends
fig2b <- artis_region_method %>% 
    mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))) %>%
  ggplot(aes(x = year, y = live_weight_t/1000000, fill = habitat_method)) +
  geom_area() +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_continuous(position = "right") +
  labs(x = "", y = "", color = "Ave. annual change in export \n(1000 t live weight)",
       fill = "Source") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        legend.position = "none",
        strip.background = element_blank(),
        plot.margin = margin(t = 6, r = 7, l = 6, unit = "mm")) +
  facet_grid(rows = vars(exporter_region), cols = vars(importer_region), 
             labeller = label_wrap_gen(width = 5), scales = "free", switch = "y")

fig2b <- ggdraw(fig2b) +
  draw_label("Exporting region", x = 0.02, y = 0.5, angle = 90, size = 10) +
  draw_label("Importing region", x = 0.5, y = 0.965, size = 10) +
  draw_label("Trade (million t, live weight)", x = 0.96, y = 0.5, angle = 270, size = 10)

fig2b
```

```{r fig2, fig.height=8, fig.width=6.5}
# Overall Figure 2
ggarrange(ggarrange(fig2a, NULL,
                    ncol = 2, nrow = 1,
                    widths = c(4.5, 0.2), labels = c("a", "")), 
          fig2b, labels = c("", "b"),
          ncol = 1, heights = c(3, 4))

ggsave(file.path(outdir, "fig2.png"))
```

# Figure 3
```{r fig3a}
# Global per capita supply
fig3a_data <- read.csv(file.path(datadir, "fig3a_data.csv"))

fig3a <- fig3a_data %>%
  # Set factor levels
  mutate(habitat_method = factor(habitat_method, levels = c("marine capture", "inland capture",
                                                            "marine aquaculture", "inland aquaculture",
                                                            "unknown" ))) %>%
  ggplot(aes(x = year, y = supply_per_cap, color = habitat_method)) +
  geom_line() + 
  labs(y = "Per capita supply (kg)", x = "", color = "Source") +
  scale_color_manual(values = habitat_source_colors) +
  guides(color = guide_legend(nrow = 1)) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

@@

```{r fig3b}
# Per capita supply by region
fig3b_data <- read.csv(file.path(datadir, "fig3b_data.csv"))

fig3b <- fig3b_data %>%
   # Set factor levels
  mutate(habitat_method = factor(habitat_method, levels = c("marine capture", "inland capture",
                                                            "marine aquaculture", "inland aquaculture",
                                                            "unknown" ))) %>%
  ggplot(aes(x = year, y = supply_per_cap, fill = habitat_method)) +
  geom_area() + 
  labs(y = "Per capita supply (kg)", x = "", fill = "Source") +
  scale_fill_manual(values = habitat_source_colors) +
  guides(fill = guide_legend(nrow = 1)) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        strip.background = element_blank()) +
  facet_wrap(~region)

@@

```{r fig3c}
# Global percent of supply by domestic / foreign exports
fig3c_data <- read.csv(file.path(datadir, "fig3c_data.csv"))

fig3c <- ggplot() +
  geom_line(data = fig3c_data, aes(x = year, y = supply_percent, color = supply_source)) +
  scale_color_manual(values = c("#F37542", "#0F2D59")) +
  labs(x = "", y = "Percent of supply", color = "Origin") +
  lims(y = c(0,100)) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

fig3c
```

```{r fig3d}
fig3d_data <- read.csv(file.path(datadir, "fig3d_data.csv"))

fig3d <- fig3d_data %>%
  ggplot(aes(x = year, y = supply_percent, color = supply_source)) +
  geom_line() +
  scale_color_manual(values = c("#F37542", "#0F2D59")) +
  labs(x = "", y = "Percent of supply", color = "Origin") +
  facet_wrap(~region) +
  lims(y = c(0,100)) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        strip.background = element_blank())

fig3d
```

```{r fig3, fig.height = 6, fig.width = 7}
fig3 <- ggarrange(
  ggarrange(fig3a, fig3b, 
            common.legend = TRUE, nrow = 1, widths = c(1, 2),
            labels = c("a", "b")),
  ggarrange(fig3c, fig3d,
            common.legend = TRUE, nrow = 1, widths = c(1, 2),
            labels = c("c", "d")),
  nrow = 2
)

fig3

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(countrycode)
library(circlize)
library(here)
library(ggpubr)
library(kableExtra)
library(DBI)
library(janitor)
library(viridis)
library(broom)
library(exploreARTIS)
library(vegan)
library(tidytext)
library(cowplot)
library(scales)
library(ggsankey)
library(ggpubr)
library(rnaturalearth)
library(CoordinateCleaner)
```

```{r load_data}
# Set directories
datadir <- "qa/manuscript_archive/manuscript_inputs"
outdir <- "qa/manuscript_archives/figures"
```

@@

region6_palette <- c(
  "#741A32", # maroon
  "#B34232", # burnt orange
  "#D38F35", #  orange
  "#D4B95F", # khaki
  "#4FA2A2", # teal
  "#114F59" # dark teal
)

@@

fig1c_out_degree <- fig1c_data %>%
    mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))) %>%
  ggplot(aes(x = year, y = all_out_degree, color = habitat_method)) +
  geom_smooth(alpha = 0.2) +
  scale_color_manual(values = habitat_source_colors) +
  labs(y = "Average\nno. export partners", color = "Source") + 
  theme_bw() +
  theme(
    text = element_text(size = 10),
    axis.title.x = element_blank(),
    legend.title = element_text(size = 7),
    legend.text = element_text(size = 6)
  )

@@

ggsave(file.path(outdir, "fig1.png"))
# ggsave(file.path(outdir, "fig1.pdf"), device = "pdf", height = )
```

# Figure 2: Foreign consumption trends
```{r foreign_consumption_setup}
marine_cap_foreign_consumption <- read.csv(file.path(datadir, "marine_capture_foreign_consumption.csv"))

marine_aqua_foreign_consumption <- read.csv(file.path(datadir, "marine_aquaculture_foreign_consumption.csv"))

inland_cap_foreign_consumption <- read.csv(file.path(datadir, "inland_capture_foreign_consumption.csv"))

inland_aqua_foreign_consumption <- read.csv(file.path(datadir, "inland_aquaculture_foreign_consumption.csv"))

marine_cap_sciname <- read.csv(file.path(datadir, "marine_capture_top_scinames_foreign_consumption.csv"))

marine_aqua_sciname <- read.csv(file.path(datadir, "marine_aquaculture_top_scinames_foreign_consumption.csv"))

inland_cap_sciname <- read.csv(file.path(datadir, "inland_capture_top_scinames_foreign_consumption.csv"))

inland_aqua_sciname <- read.csv(file.path(datadir, "inland_aquaculture_top_scinames_foreign_consumption.csv"))

# Load world map data
world <- ne_countries(scale = "medium", returnclass = "sf") %>%
  filter(iso_a3 != "ATA")

consumer_map_df <- marine_cap_foreign_consumption %>%
  mutate(habitat_method = "Marine Capture") %>%
  bind_rows(marine_aqua_foreign_consumption %>%
              mutate(habitat_method = "Marine Aquaculture")) %>%
  bind_rows(inland_cap_foreign_consumption %>%
              mutate(habitat_method = "Inland Capture")) %>%
  bind_rows(inland_aqua_foreign_consumption %>%
              mutate(habitat_method = "Inland Aquaculture")) %>%
  group_by(consumer_iso3c, habitat_method) %>%
  summarize(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>%
  ungroup() %>%
  left_join(
    world,
    by = c("consumer_iso3c"="iso_a3")
  )

country_centroids <- countryref %>%
  filter(str_count(as.character(adm1_code))==3) %>%
  group_by(iso3) %>%
  summarise(centroid.lon = mean(centroid.lon),
            centroid.lat = mean(centroid.lat)) %>%
  ungroup() %>%
  mutate(
    centroid.lon = case_when(
      iso3 == "KIR" ~ 172.9717,
      TRUE ~ centroid.lon
    ),
    centroid.lat = case_when(
      iso3 == "KIR" ~ 1.4518,
      TRUE ~ centroid.lat
    )
  )

trade_map <- ggplot(world) +
  geom_sf(size = 0.1, color = "white", fill = "grey", alpha = 0.5)

# Maximum and minimum limits for maps and stacked bar charts
consumption_live_magnitude <- 1e6

map_min <- 0
map_max <- max(consumer_map_df$consumption_live_t, na.rm = TRUE) / consumption_live_magnitude
arrows_min <- 0
arrows_max <- max(
  c(marine_cap_foreign_consumption$consumption_live_t,
    marine_aqua_foreign_consumption$consumption_live_t,
    inland_cap_foreign_consumption$consumption_live_t,
    inland_aqua_foreign_consumption$consumption_live_t),
  na.rm = TRUE
) / consumption_live_magnitude

sciname_df <- marine_cap_sciname %>%
  mutate(habitat_method = "Marine Capture") %>%
  bind_rows(marine_aqua_sciname %>%
              mutate(habitat_method = "Marine Aquaculture")) %>%
  bind_rows(inland_cap_sciname %>%
              mutate(habitat_method = "Inland Capture")) %>%
  bind_rows(inland_aqua_sciname %>%
              mutate(habitat_method = "Inland Aquaculture")) %>%
  group_by(common_name, flow, habitat_method) %>%
  summarize(consumption_live_t = sum(consumption_live_t, na.rm = TRUE)) %>%
  ungroup()

stacked_bar_min <- 0
stacked_bar_max <- max(
  sciname_df$consumption_live_t,
  na.rm = TRUE
) / consumption_live_magnitude

```{r marine_cap_foreign_consumption}

marine_cap_map <- trade_map +
  geom_sf(data = consumer_map_df %>%
            filter(habitat_method == "Marine Capture"), 
          aes(fill = consumption_live_t/consumption_live_magnitude, geometry = geometry), color = "white", size = 0.1) +
  scale_fill_gradient(low = "#86ADA7", high = "#0F2D59", limits=c(map_min, map_max)) +
  theme_bw() + 
  theme(
    legend.position = "none",
    axis.title = element_blank(),
    axis.ticks = element_blank(),
    axis.text = element_blank(),
    panel.grid.major = element_blank(),
    panel.background = element_blank(),
    panel.spacing = unit(2, "mm"),
    panel.border = element_blank(),
    plot.background = element_blank(),
    plot.margin = unit(c(0,0,-5,0),"mm")
  )

marine_cap_arrows <- marine_cap_foreign_consumption %>%
  slice_max(n = 10, order_by = consumption_live_t) %>%
  # Join with lat/long data for centroids
  left_join(country_centroids, by = c("source_country_iso3c" = "iso3")) %>%
  left_join(country_centroids, by = c("consumer_iso3c" = "iso3")) %>%
  mutate(centroid.lat.x = 1.05 * centroid.lat.x,
         centroid.lat.y = 0.95 * centroid.lat.y)

marine_cap_map <- marine_cap_map +
  geom_curve(data = marine_cap_arrows, 
                 aes(x = centroid.lon.x, y = centroid.lat.x, 
                     xend = centroid.lon.y, yend = centroid.lat.y,
                     color = consumption_live_t/consumption_live_magnitude),
                 size = 1.2,
                 alpha = 0.75,
                 curvature = -0.35, arrow = arrow(length = unit(3, "mm"), angle = 20)) +
      scale_colour_gradient(low = "#F7AF75", high = "#E24027", limits = c(arrows_min, arrows_max))

marine_cap_map

marine_cap_stacked_bar <- marine_cap_sciname %>%
  mutate(common_name = case_when(
    common_name == "alaska pollock(=walleye poll.)" ~ "alaska pollock",
    TRUE ~ common_name
  )) %>%
  mutate(common_name = gsub(" ", "\n", common_name)) %>%
  mutate(common_name = reorder(common_name, desc(total))) %>%
  ggplot(aes(x = consumption_live_t/consumption_live_magnitude, y = flow, fill = region)) +
  geom_bar(stat = "identity", position = "stack", width = 0.8) +
  scale_fill_manual(values = region6_palette) +
  labs(x = "", y = "") +
  lims(x = c(stacked_bar_min, stacked_bar_max)) +
  facet_grid(vars(common_name), switch = "y") +
  theme_minimal() +
  theme(
    strip.text.y.left = element_text(size = 8),
    strip.placement = "outside",
    legend.position = "none",
    panel.spacing = unit(2, "mm"),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 8),
    plot.margin = unit(c(0, 5, -5, -10), "mm")
  )

marine_cap_stacked_bar

marine_cap <- ggarrange(
  marine_cap_map, marine_cap_stacked_bar,
  nrow = 1, ncol = 2,
  widths = c(1.5, 1)
)

marine_cap <- annotate_figure(
  marine_cap, top = text_grob("Marine Capture")#, vjust = 1),
)

marine_cap

# ggsave(file.path(outdir, "marine_cap_map_bar.png"), width = 6, height = 3, dpi = 300, units = "in", device = "png")
```

```{r marine_aqua_foreign_consumption}
marine_aqua_map <- trade_map +
  geom_sf(data = consumer_map_df %>%
            filter(habitat_method == "Marine Aquaculture"), 
          aes(fill = consumption_live_t/consumption_live_magnitude, geometry = geometry), color = "white", size = 0.1) +
  scale_fill_gradient(low = "#86ADA7", high = "#0F2D59", limits = c(map_min, map_max)) +
  theme_bw() + 
  theme(
    legend.position = "none",
    axis.title = element_blank(),
    axis.ticks = element_blank(),
    axis.text = element_blank(),
    panel.grid.major = element_blank(),
    panel.background = element_blank(),
    panel.spacing = unit(2, "mm"),
    panel.border = element_blank(),
    plot.background = element_blank(),
    plot.margin = unit(c(0,0,-5,0),"mm")
  )

marine_aqua_arrows <- marine_aqua_foreign_consumption %>%
  slice_max(n = 10, order_by = consumption_live_t) %>%
  # Join with lat/long data for centroids
  left_join(country_centroids, by = c("source_country_iso3c" = "iso3")) %>%
  left_join(country_centroids, by = c("consumer_iso3c" = "iso3")) %>%
  mutate(centroid.lat.x = 1.05 * centroid.lat.x,
         centroid.lat.y = 0.95 * centroid.lat.y)

marine_aqua_map <- marine_aqua_map +
  geom_curve(data = marine_aqua_arrows, 
                 aes(x = centroid.lon.x, y = centroid.lat.x, 
                     xend = centroid.lon.y, yend = centroid.lat.y,
                     color = consumption_live_t/consumption_live_magnitude),
                 size = 1.2,
                 alpha = 0.75,
                 curvature = -0.35, arrow = arrow(length = unit(3, "mm"), angle = 20)) +
      scale_colour_gradient(low = "#F7AF75", high = "#E24027", limits = c(arrows_min, arrows_max))

marine_aqua_map

marine_aqua_stacked_bar <- marine_aqua_sciname %>%
  mutate(common_name = gsub(" ", "\n", common_name))%>%
  mutate(common_name = reorder(common_name, desc(total))) %>%
  ggplot(aes(x = consumption_live_t/consumption_live_magnitude, y = flow, fill = region)) +
  geom_bar(stat = "identity", position = "stack", width = 0.8) +
  scale_fill_manual(values = region6_palette) +
  labs(x = "", y = "") +
  lims(x = c(stacked_bar_min, stacked_bar_max)) +
  facet_grid(vars(common_name), switch = "y") +
  theme_minimal() +
  theme(
    strip.text.y.left = element_text(size = 8),
    strip.placement = "right",
    legend.position = "none",
    panel.spacing = unit(2, "mm"),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    plot.margin = unit(c(0, 5, -5, -10), "mm")
  )

marine_aqua_stacked_bar

marine_aqua <- ggarrange(
  marine_aqua_map, marine_aqua_stacked_bar,
  nrow = 1, ncol = 2,
  widths = c(1.5, 1)
)

marine_aqua <- annotate_figure(
  marine_aqua, top = text_grob("Marine Aquaculture")#, vjust = 1),
)

marine_aqua

# ggsave(file.path(outdir, "test.png"), width = 6, height = 3, dpi = 300, units = "in", device = "png")
```

```{r inland_cap_foreign_consumption}

inland_cap_map <- trade_map +
  geom_sf(data = consumer_map_df %>%
            filter(habitat_method == "Inland Capture"), 
          aes(fill = consumption_live_t/consumption_live_magnitude, geometry = geometry), color = "white", size = 0.1) +
  scale_fill_gradient(low = "#86ADA7", high = "#0F2D59", limits = c(map_min, map_max)) +
  theme_bw() + 
  theme(
    legend.position = "none",
    axis.title = element_blank(),
    axis.ticks = element_blank(),
    axis.text = element_blank(),
    panel.grid.major = element_blank(),
    panel.background = element_blank(),
    panel.spacing = unit(2, "mm"),
    panel.border = element_blank(),
    plot.background = element_blank(),
    plot.margin = unit(c(0,0,-5,-10),"mm")
  )

inland_cap_arrows <- inland_cap_foreign_consumption %>%
  slice_max(n = 10, order_by = consumption_live_t) %>%
  # Join with lat/long data for centroids
  left_join(country_centroids, by = c("source_country_iso3c" = "iso3")) %>%
  left_join(country_centroids, by = c("consumer_iso3c" = "iso3")) %>%
  mutate(centroid.lat.x = 1.05 * centroid.lat.x,
         centroid.lat.y = 0.95 * centroid.lat.y)

inland_cap_map <- inland_cap_map +
  geom_curve(data = inland_cap_arrows, 
                 aes(x = centroid.lon.x, y = centroid.lat.x, 
                     xend = centroid.lon.y, yend = centroid.lat.y,
                     color = consumption_live_t/consumption_live_magnitude),
                 size = 1.2,
                 alpha = 0.75,
                 curvature = -0.35, arrow = arrow(length = unit(3, "mm"), angle = 20)) +
      scale_colour_gradient(low = "#F7AF75", high = "#E24027", limits = c(arrows_min, arrows_max))

inland_cap_map

inland_cap_stacked_bar <- inland_cap_sciname %>%
  mutate(common_name = gsub(" nei", "", common_name)) %>%
  mutate(common_name = case_when(
    common_name == "ray-finned fishes" ~ "\nray-finned fishes",
    common_name == "freshwater siluroids" ~ "\nfreshwater siluroids",
    common_name == "nile perch" ~ "\nnile perch",
    TRUE ~ common_name
  )) %>%
  mutate(common_name = gsub(" ", "\n", common_name)) %>%
  mutate(common_name = reorder(common_name, desc(total))) %>%
  ggplot(aes(x = consumption_live_t/consumption_live_magnitude, y = flow, fill = region)) +
  geom_bar(stat = "identity", position = "stack", width = 0.8) +
  scale_fill_manual(values = region6_palette) +
  labs(x = "", y = "") +
  lims(x = c(stacked_bar_min, stacked_bar_max)) +
  facet_grid(vars(common_name), switch = "y") +
  theme_minimal() +
  theme(
    strip.text.y.left = element_text(size = 8),
    strip.placement = "outside",
    legend.position = "none",
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    panel.spacing = unit(2, "mm"),
    plot.margin = margin(r = 5, l=-10, b=-5, unit="mm")# unit(c(, 5, 0, -10), "mm")
  )

inland_cap_stacked_bar

inland_cap <- ggarrange(
  inland_cap_map, inland_cap_stacked_bar,
  nrow = 1, ncol = 2,
  widths = c(1.5, 1)
)

inland_cap <- annotate_figure(
  inland_cap, top = text_grob("Inland Capture")#, vjust = 1),
)

inland_cap

# ggsave(file.path(outdir, "test.png"), width = 6, height = 3, dpi = 300, units = "in", device = "png")
```

```{r inland_aqua_foreign_consumption}
inland_aqua_map <- trade_map +
  geom_sf(data = consumer_map_df %>%
            filter(habitat_method == "Inland Aquaculture"), 
          aes(fill = consumption_live_t/consumption_live_magnitude, geometry = geometry), color = "white", size = 0.1) +
  scale_fill_gradient(low = "#86ADA7", high = "#0F2D59", limits = c(map_min, map_max)) +
  theme_bw() + 
  theme(
    legend.position = c(0.5, 0.05),
    legend.direction = "horizontal",
    legend.box = "vertical",
    legend.spacing.y = unit(1, "mm"),
    legend.spacing.x = unit(5, "mm"),
    legend.title = element_text(size = 10),
    legend.box.margin = margin(b = 3, t = 10, r = 20, unit = "mm"),
    legend.margin = margin(t = 0, unit = "mm"),
    axis.title = element_blank(),
    axis.ticks = element_blank(),
    axis.text = element_blank(),
    panel.grid.major = element_blank(),
    panel.background = element_blank(),
    panel.spacing = unit(2, "mm"),
    panel.border = element_blank(),
    plot.background = element_blank(),
    legend.key.height = unit(2.5, "mm"),
    plot.margin = margin(t=-10, unit="mm")
  )

inland_aqua_arrows <- inland_aqua_foreign_consumption %>%
  slice_max(n = 10, order_by = consumption_live_t) %>%
  # Join with lat/long data for centroids
  left_join(country_centroids, by = c("source_country_iso3c" = "iso3")) %>%
  left_join(country_centroids, by = c("consumer_iso3c" = "iso3")) %>%
  mutate(centroid.lat.x = 1.05 * centroid.lat.x,
         centroid.lat.y = 0.95 * centroid.lat.y)

inland_aqua_map <- inland_aqua_map +
  geom_curve(data = inland_aqua_arrows, 
                 aes(x = centroid.lon.x, y = centroid.lat.x, 
                     xend = centroid.lon.y, yend = centroid.lat.y,
                     color = consumption_live_t/consumption_live_magnitude),
                 size = 1.2,
                 alpha = 0.75,
                 curvature = -0.35, arrow = arrow(length = unit(3, "mm"), angle = 20)) +
      scale_colour_gradient(low = "#F7AF75", high = "#E24027", limits = c(arrows_min, arrows_max)) +
  labs(fill = "Consumption (mil. t.)",
       colour = "Export (mil. t.)           ")

inland_aqua_map

inland_aqua_stacked_bar <- inland_aqua_sciname %>%
  mutate(common_name = gsub(" nei", "", common_name)) %>%
  mutate(common_name = case_when(
    common_name == "ray-finned fishes" ~ "\nray-finned fishes",
    common_name == "striped catfish" ~ "\nstriped catfish",
    common_name == "freshwater siluroids" ~ "\nfreshwater siluroids",
    common_name == "nile tilapia" ~ "\nnile tilapia",
    TRUE ~ common_name
  )) %>%
  mutate(common_name = gsub(" ", "\n", common_name)) %>%
  mutate(common_name = reorder(common_name, desc(total))) %>%
  mutate(region = case_when(
    region == "North America" ~ "N. America",
    region == "South America" ~ "S. America",
    TRUE ~ region
  )) %>%
  ggplot(aes(x = consumption_live_t/consumption_live_magnitude, y = flow, fill = region)) +
  geom_bar(stat = "identity", position = "stack", width = 0.8) +
  scale_fill_manual(values = region6_palette) +
  labs(x = "", y = "", fill = "") +
  lims(x = c(stacked_bar_min, stacked_bar_max)) +
  facet_grid(vars(common_name), switch = "y") +
  theme_minimal() +
  theme(
    strip.placement = "outside",
    strip.text.y.left = element_text(size = 8),
    legend.position = "bottom",
    legend.box = "horizontal",
    legend.text = element_text(size = 8),
    legend.key.size = unit(3, "mm"),
    legend.box.margin = margin(l = -25, unit = "mm"),
    legend.margin = margin(t = -7, b = 0, unit = "mm"),
    panel.spacing = unit(2, "mm"),
    plot.margin = unit(c(0, 5, 0, -10), "mm")
  )

inland_aqua_stacked_bar

inland_aqua <- ggarrange(
  inland_aqua_map, inland_aqua_stacked_bar,
  nrow = 1, ncol = 2,
  widths = c(1.5, 1))

inland_aqua <- annotate_figure(
  inland_aqua, top = text_grob("Inland Aquaculture")
)

inland_aqua

ggsave(file.path(outdir, "test.png"), width = 6, height = 3, dpi = 300, units = "in", device = "png")
```

```{r foreign_consumption, fig.height = 15, fig.width = 8}
ggarrange(marine_cap,
          marine_aqua,
          inland_cap,
          inland_aqua,
          ncol = 1,
          heights = c(1, 1, 1, 1.1),
          common.legend = TRUE)

ggsave(file.path(outdir, "fig2.png"), width = 9, height = 13, dpi = 500, unit = "in", device = "png")
```

# Figure 3: Trade patterns

```{r fig3_data}
artis_region_method <- read.csv(file.path(datadir, "fig_3_data.csv"))
```

```{r fig3a}
region_net_import <- artis_region_method %>% 
  group_by(year, importer_region) %>%
  summarise(import_live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>%
  rename(region = importer_region) %>%
  left_join(artis_region_method %>% 
              group_by(year, exporter_region) %>%
              summarise(export_live_weight_t = sum(live_weight_t, na.rm = TRUE)) %>%
              rename(region = exporter_region), by = c("year", "region")) %>%
  mutate(net_import = import_live_weight_t-export_live_weight_t)

fig3a <- ggplot() +
  geom_area(data = artis_region_method %>% 
                mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))) %>%
              select(-exporter_importer) %>%
              pivot_longer(exporter_region:importer_region, 
                           names_to = c("flow", "drop"), 
                           values_to = "region", names_sep = "_") %>% 
              filter(flow == "exporter") %>%
              group_by(year, region, habitat_method) %>%
              summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)), 
            aes(x = year, y = -1*live_weight_t/1000000, fill = habitat_method)) +
  geom_area(data = artis_region_method %>% 
                mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))) %>%
              select(-exporter_importer) %>%
              pivot_longer(exporter_region:importer_region, 
                           names_to = c("flow", "drop"), 
                           values_to = "region", names_sep = "_") %>% 
              filter(flow == "importer") %>%
              group_by(year, region, habitat_method) %>%
              summarise(live_weight_t = sum(live_weight_t, na.rm = TRUE)), 
            aes(x = year, y = live_weight_t/1000000, fill = habitat_method)) +
  scale_fill_manual(values = habitat_source_colors) +
  geom_hline(yintercept = 0, color = "black", linewidth = 0.5, linetype = "dashed") +
  geom_line(data = region_net_import, aes(x = year, y = net_import/1000000, color = "Net import"), linewidth = 1) +
  scale_color_manual(values = "black") +
  labs(x = "", y = "Trade (million t, live weight)", fill = "Source", color = "") +
  guides(fill = guide_legend(nrow = 2)) +
  theme_bw() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        strip.background = element_blank(),
        plot.margin = unit(c(t=0, r=1, b=0, l=0.5), "cm")) +
  facet_wrap(~region, nrow = 1)

fig3a <- ggdraw(fig3a) +
  draw_label("Net import", x = 0.97, y = 0.55, angle = 270, size = 9) +
  draw_label("Net export", x = 0.97, y = 0.3, angle = 270, size = 9)

@@

```{r fig3b}
# Matrix of plots showcasing inter-regional trade trends
fig3b <- artis_region_method %>% 
    mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))) %>%
  ggplot(aes(x = year, y = live_weight_t/1000000, fill = habitat_method)) +
  geom_area() +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_continuous(position = "right") +
  labs(x = "", y = "", color = "Ave. annual change in export \n(1000 t live weight)",
       fill = "Source") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        legend.position = "none",
        strip.background = element_blank(),
        plot.margin = margin(t = 6, r = 7, l = 6, unit = "mm")) +
  facet_grid(rows = vars(exporter_region), cols = vars(importer_region), 
             labeller = label_wrap_gen(width = 5), scales = "free", switch = "y")

fig3b <- ggdraw(fig3b) +
  draw_label("Exporting region", x = 0.02, y = 0.5, angle = 90, size = 10) +
  draw_label("Importing region", x = 0.5, y = 0.965, size = 10) +
  draw_label("Trade (million t, live weight)", x = 0.96, y = 0.5, angle = 270, size = 10)

@@

```{r fig3, fig.height=8, fig.width=6.5}
# Overall Figure 3
ggarrange(ggarrange(fig3a, NULL,
                    ncol = 2, nrow = 1,
                    widths = c(4.5, 0.2), labels = c("a", "")), 
          fig3b, labels = c("", "b"),
          ncol = 1, heights = c(3, 4))

@@

# Figure 3: Foreign consumption maps and top species traded

# Figure 4
```{r fig4a}
# Global per capita supply
fig4a_data <- read.csv(file.path(datadir, "fig_4a_data.csv"))

fig4a <- fig4a_data %>%
  # Set factor levels
  mutate(habitat_method = factor(habitat_method, levels = c("marine capture", "inland capture",
                                                            "marine aquaculture", "inland aquaculture",
                                                            "unknown" ))) %>%
  ggplot(aes(x = year, y = supply_per_cap, color = habitat_method)) +
  geom_line() + 
  labs(y = "Per capita supply (kg)", x = "", color = "Source") +
  scale_color_manual(values = habitat_source_colors) +
  guides(color = guide_legend(nrow = 1)) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

fig4a
```

```{r fig4b}
# Per capita supply by region
fig4b_data <- read.csv(file.path(datadir, "fig_4b_data.csv"))
